### 2020-10-07 doc/manuscript/Dow_manuscript.Rmd
Done Figure 6

---
title: ''
output: word_document
bibliography: references.bib
csl: global-change-biology.csl #(this will change depending on journal we choose. GCB would be a great choice)
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r logistic-growth-model, out.width="100%", echo=FALSE, fig.align="center", fig.cap="Lorem ipsum"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig1.png")
```

>>>>

---
title: ''
output: 
  word_document: 
    fig_caption: yes
bibliography: references.bib
csl: global-change-biology.csl #(this will change depending on journal we choose. GCB would be a great choice)
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Figure 1** 
```{r fig1, out.width="100%", echo=FALSE, fig.align="center", fig.cap= "Logistic growth model"}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/fig1.png")
```

**Figure 6**

Notes for now:

1. Model was fit to a random sample of 20 out of 106 tags to speed up computation.
1. Climwin mean temperatures are recentered at 65F to help sanity check intercepts and slopes. 65F was chosen because it is a "typical" climwinmean value
1. The multivariate model for $(DOY_{25}, DOY_{50}, DOY_{75})$ has:
    1. Fixed effects: The interaction between wood type (diffuse vs ring porous) and climwin mean
    1. Random effects: tag number (no species just yet)

```{r, echo = FALSE}
fig6_caption <- "Relationship between DOY and climwin mean tempeatures. For each 
observed climwin mean temperature value, the posterior mean of the fitted day of year
is represented by the solid blue line and credible intervals are represented by bands."
```

```{r fig6, out.width="100%", echo=FALSE, fig.align="center", fig.cap=fig6_caption}
# Created in RScripts/bert/wood_phenology_analysis_bert.R
knitr::include_graphics("tables_figures/fig6.png")
```
